---
title: "Measures of Dispersion"
author: "Naveen N"
date: "2023-10-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Basic Statistics
Range - Max - Min
Inter-Quartile : Q3 - Q1
Outliers = Q1 - 1.5 * IQR or 
         = Q3 + 1.5 * IQR

# Box PLot - 
*  used when describing center and variability of data
*  useful for detecting outtliers

# sd = sqrt(variance)
# Coefficinet of Variance
# CV = (sd/mean)*100
# Skewness 
* Postive
* Negative
# Formula :-
#(Mean - Mode)/sd
# 3 * (Median - Mode)/sd

# Skewness == 0 - symmetrice
# Skewness
*  -0.5 to 0.5 : Approximately Symmetric
* -1 to 1      : Moderately  Skewed
* >1 or <-1    : Highly Skewed

# Kurtosis
* Lepto  >3
* Meso   =3
* Platy  <3

# A scatterplot is useful for eyeballing the presence of outliers

# Covariance and Correlation


if cov > 0 -> Directly Proportional(Positively Correlated)
if cov < 0 -> Inversely Proportional(Negatively Correlated)
if cov == 0 -> Uncorrelated

#Correlation Matrix
A correlation matrix is essentially a table depicting the correlation coefficients for various variables. The rows and columns contains the value of the variables and each cell shows the correlation coefficient


```{r}
rm(list = ls())
```
```{r}
library(MASS)
```
```{r}
newg = na.omit(geyser)
View(newg)
```
```{r}
newf= na.omit(faithful)
View(newf)
```

#Mean
```{r}
duration = newf$eruptions
round(mean(duration),2)
```
#Median
```{r}
Q2 = median(newf$eruptions)
Q2
```

#Quantile
```{r}
quantile(duration)
```
```{r}
quantile(duration,c(0.75,.80))
```
#Range
```{r}
quantile(duration,.100) - quantile(duration,0.0)
```
#IQR
```{r}
Q3 = quantile(duration,0.75)
Q1 = quantile(duration,0.25)
IQR = Q3 - Q1 
IQR

```
#Variance
```{r}
var(duration)
```
#Central Moments
```{r}
library(e1071)
```
#Order 3
```{r}
moment(duration,order = 3,center = TRUE)
```

#Skewness
```{r}
skewness(duration)
```

#Kurtosis
```{r}
kurtosis(duration)
```

#Correlation and Covariance
```{r}
cor(duration,newf$waiting)
cov(duration, newf$waiting)
```

