---
title: "Control Statements"
author: "N Naveen"
date: "2023-10-28"
output:
  pdf_document: default
  html_document: default
editor_options:
  markdown:
    wrap: 72
---

#Control statements in R #used to control the execution and flow of the
program based on the condition #used to make decisions after assessing
the variable #- if condition \# - else condition \# - for loop \# -
while loop \# - repeat and break statement \# - return statement \# -
next statement -\> continue


#for loop
#for(value in vector)
#{
# statements......}
```{r}
for ( i in 1:4)
{   print(i^2)}

```

```{r}
x <- letters[4:10]
for (i in x)
{
  print(i)
}
```


#Input / Output
#readline() - takes input in string format
#Can convert inputted value using "as" keyword


```{r}
#Syntax
var1 = readline("Enter a number:");
var1 = as.integer(var1)
var1
```

```{r}
cat(var1)
message(var1)
```


#Print function in R
#cat() - converts arguments to character strings
#message() - 

#1.Write a program in R for fibonacci series upto n numbers
```{r}
n = readline("Enter the value of n :")
n = as.integer(n)
fibo = c(0,1)
sum = 1
for (i in 3:n)
{
  fibo[i] = fibo[i-1] + fibo[i-2]
  sum = sum  + fibo[i]
}
cat("sum upto",n,"of fibonacci series is",sum)
```

#2.Print the number of vowels and consonants present in your name.
```{r}

x = readline("Enter your name:")
summ = 0
vowels = c("a","i","e","o","u")
for (char in strsplit(x, "")[[1]])
{
  if (char %in% vowels)
  {
    summ = summ + 1
  }
}
cons = nchar(x) - summ
cat("No of vowels:",summ,"\n")

cat("No of consonants:",cons)
```

#3. Given a number, write r script to print the pairwise factors of the given number.
```{r}

n = readline("Enter the number:")
n = as.integer(n)
for (i in 1:n)
{
  if(n%%i == 0)
  {
    cat(i,n/i,"\n")
  }
}
```


#4.Write a program to generate any 10 random numbers between 10 and 100 and then create
#two vectors to store the odd and even numbers.
```{r}

even = c()
odd = c()
for (i in 1:10)
{
  x = sample(10:100,1)
  if (x%%2 == 0)
  {
    even  = append(even,x)
  }else
  {
    odd = append(odd,x)
  }
}
cat("Even vector\n",even)
cat("\nOdd vector\n",odd)
```

#5.Find the strength of the given password. The password is strong if it satisfies all the below
#conditions. A moderate password is one that satisfies first three conditions and #has length atleast 6, 
#otherwise password is week.
# It contains at least one lowercase English character.
# It contains at least one uppercase English character.
# It contains at least one special character. The special characters are: !@#$%^&*()-+
# Its length is at least 8.
# It contains at least one digit.
```{r}

x = readline("Enter the password:")
chrr = strsplit(x,"")[[1]]

c1  = FALSE
c2 = FALSE
c3 = FALSE
c4 = FALSE
c5 = FALSE

sp = c("!","@","#","$","%","^","&","*","(",")","-","+")

for(i in chrr)
{
  if(i %in% LETTERS)
     
  {
    c1 = TRUE    
  }
  if(i %in% tolower(letters))
  {
    c2 = TRUE
  }
  if(i %in% sp)
  {
    c3 = TRUE
  }
  if(length(chrr) >= 8)
  {
    c4 = TRUE
  }
  if(i %in% c(0,1,2,3,4,5,6,7,8,9)){
    c5 = TRUE
  }
}



if(length(chrr) >= 6 && c1 == TRUE && c2 == TRUE && c3 == TRUE){
  if(c4 == TRUE && c5 == TRUE)
  {
    cat("Password is Strong")
  }else
  {
    cat("Password is Moderate")
  }
}else
{
  cat("Password is weak")
}
```
