---
title: "Measures of Dispersion"
author: "Naveen N"
date: "2023-10-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Basic Statistics
Range - Max - Min
Inter-Quartile : Q3 - Q1
Outliers = Q1 - 1.5 * IQR or 
         = Q3 + 1.5 * IQR

# Box PLot - 
*  used when describing center and variability of data
*  useful for detecting outtliers

# sd = sqrt(variance)
# Coefficinet of Variance
# CV = (sd/mean)*100
# Skewness 
* Postive
* Negative
# Formula :-
#(Mean - Mode)/sd
# 3 * (Median - Mode)/sd

# Skewness == 0 - symmetric
# Skewness
*  -0.5 to 0.5 : Approximately Symmetric
* -1 to 1      : Moderately  Skewed
* >1 or <-1    : Highly Skewed

# Kurtosis
* Lepto  >3
* Meso   =3
* Platy  <3

# A scatterplot is useful for eyeballing the presence of outliers

# Covariance and Correlation


if cov > 0 -> Directly Proportional(Positively Correlated)
if cov < 0 -> Inversely Proportional(Negatively Correlated)
if cov == 0 -> Uncorrelated

#Correlation Matrix
A correlation matrix is essentially a table depicting the correlation coefficients for various variables. The rows and columns contains the value of the variables and each cell shows the correlation coefficient


```{r}
rm(list = ls())
```
```{r}
library(MASS)
```
```{r}
newg = na.omit(geyser)
View(newg)
```
```{r}
newf= na.omit(faithful)
View(newf)
```

#Mean
```{r}
duration = newf$eruptions
cat("Mean of the eruptions is ",round(mean(duration),2))

```
#Median
```{r}
Q2 = median(newf$eruptions)
Q2
cat("Median of the eruptions is ",Q2)
```

#Quantile
```{r}
cat("The Quantiles of the duration\n",quantile(duration))
```
```{r}
cat("The Quantiles of the duration of 75% and 80% are \n",quantile(duration,c(0.75,.80)))
```
#Range
```{r}
cat("The Range of Duration is ",quantile(duration,1) - quantile(duration,0.0))
```
#IQR
```{r}
Q3 = quantile(duration,0.75)
Q1 = quantile(duration,0.25)
IQR = Q3 - Q1 
IQR1 = IQR(duration)
IQR1
cat("The IQR of duration is",IQR)

```
#Variance
```{r}
cat("The variance of the duration is ",var(duration))
```
#Central Moments
```{r}
library(e1071)
```
#Order 3
```{r}
x = moment(duration,order = 3,center = TRUE)
x
cat("The central moments of duration of order 3 is ",x)
```

#Skewness
```{r}
sk = skewness(duration)
sk 
if (sk >= -0.5 && sk <= 0.5) {
  cat("The skewness of duration is Approximately Symmetric")
}else if((sk > -1.0 && sk < -0.5) && (sk > 0.5 && sk < 1.0)) {
  cat("The skewness of the duration is Moderately Skewed")
}else{
  cat("The Skewness of the duration is Highly Skewed")
}
```

#Kurtosis
```{r}
k = kurtosis(duration)
k
if(k == 3) {
  cat("The Kurtosis of the duration is Meso")
}else if(k < 3){
  cat("The Skewness of the duration is Platy")
}else if(k > 3){
  cat("The Kurtosis of the duration is Lepto")
}
```

#Correlation and Covariance
```{r}
core = cor(duration,newf$waiting)
cat("The Correlation of Duration and Wainting is",core,"\n")
if(core <= 1 && core >= -1){
  if(core == -1 || core == 1){
    cat("Duration and Wainting are Perfectly Correlated\n")
  }
  if(core > 0){
    cat("Duration and Waiting are Positively Correlated")
  }else if(core < 0){
    cat("Duration and Waiting are Negatively Correlated")
  }
}else {
  cat("Duration and Waiting are Uncorrelated")
}


```
```{r}
cova = cov(duration, newf$waiting)
cat("The covariance of duration and waiting is",cova,"\n")

if(cova > 0){
  cat("Duration and Waiting has Positive Covariance")
}else if(cova < 0){
  cat("Duration and Waiting has Negative Covariance")
}
```

