---
title: "Time Series Analysis"
author: "N Naveen"
date: "2023-11-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Time series data
* experimental data that have been observed at different points on time

### Examples
* daily stock market quotations
* monthly unemployment figures
* No of covid - 19 cases over period of time
* BP over a period of time

## Components
* Long term Movement or Trend
* Short term Movements
  * Seasonal Variations
  * Cyclic Variations
* Random or irregular Movements

## Stationary Series 


### Autoregression
  * y = b0 + b1 * X1
* By using this we can predict the values for the next time step(t+1) 

## Moving Average

### ARMA (Auto Regresssion Moving Average)
* Integration of Autoregression and Moving average

### ARIMA (Auto Regression Integrated Moving Average)


## TIME SERIES ANALYSIS
* ts()
* used to show how objects behave over a period of time

```{r}
install.packages("forecast")
```
```{r}
library(forecast)
```

```{r}

```

