---
title: "Visualization"
author: "N Naveen"
date: "2023-11-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Visualization  
* Base Graphics
* grid Graphics
* lattice Graphics
* ggplot Graphics


```{r}
library("MASS")
```

```{r}
data = na.omit(airquality)
View(data)
```


### Plotting Ozone using plot       
```{r}
plot(data$Ozone)
```
## Scatter Plot       
```{r}
plot(data$Ozone, data$Wind)
```
## Plot Freq        
```{r}
freq = table(data$Month)
plot(freq)
```
## When the scatter plot is used with entire dataset, a matrix of scatterplots is obtained which is a correlation matrix of all the columns       
```{r}
plot(data)
```

## Bar plot       
```{r}
barplot(data$Ozone, main = "Ozone levels")
```

## Hist       
```{r}
hist(data$Solar.R)
```
## Box plot       
```{r}
boxplot(data$Ozone)
```
## Multiple box plot        
```{r}
boxplot(data[,1:4],main = "Multiple Box plot")
```
## ggplot  - grammer of graphics        

```{r}
library(ggplot2)
```

## ggplot components        
* Data : data
* Aesthetics : mapping x and y
* Geometrics : what type of graph
* Facets

```{r}
ggplot(data = mtcars,aes(x = wt,y = mpg))+geom_point() 
```
## Geometrics       
* Scatter- geom_point
* Bar-  geom_bar
* Hist - geom_histogram
* Line chart - geom_line
* geom_polygon

### Scatter plot        
```{r}
ggplot(iris, aes(x = Sepal.Length, y = Petal.Length)) +geom_point() 
```
### ggplot - scatter plot       
```{r}
ggplot(iris, aes(x = Sepal.Length, y = Petal.Length,col = Species, shape = Species))+ geom_point()
```
### ggplot - scatter plot       
```{r}
ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, col = Species)) + geom_point() + geom_smooth()
```
### ggplot - scatter        
```{r}
ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, col = Species)) + geom_point(color = "blue") + geom_smooth(color = "red")
```
### ggplot - bar        
```{r}
ggplot(mtcars,aes(x = gear)) + geom_bar()
```
### ggplot - Histogram        
```{r}
ggplot(mtcars, aes(x = mpg)) + geom_histogram()
```
### Box plot        
```{r}
ggplot(mtcars, aes(x = as.factor(cyl), y= mpg))  + geom_boxplot()
```
#
```{r}

```

