---
title: "Visualization_P.Rmd"
author: "N Naveen"
date: "2023-11-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("MASS")
```

```{r}
newsurvey = na.omit(survey)
View(newsurvey)
```
```{r}
library(ggplot2)
```


##1. Plot a bar graph for the number of male and female participants in the survey. Provide
the title as “Male and Female participants”, y-axis label as “frequency” and specify
the colours for the bars.
```{r}
freq = table(newsurvey$Sex)
barplot(freq, main = "Male and Female Participants", ylab = "Frequecy", col = c("red","blue"))
```
## 2.Plot a bar graph for the number of left handers and right handers in the survey.
Provide the title as “Left Handers and Right Handers”, y-axis label as “count” and
specify the colours for the bars.
```{r}
count = table(newsurvey$W.Hnd)
barplot(count,main = "Left Handeres and Right Handers", ylab = "Count",col = c("red","blue"))
```
## 3.Plot the distribution between male left handers and female left handers using bar
chart. Provide the title as “Female Left Handers and Male Left Handers , y-axis label
as “count” and specify the colours for the bars.
```{r}
library(dplyr)
```

```{r}
d1 = newsurvey %>% filter(W.Hnd == "Left") 
count = table(d1$Sex)
barplot(count,main = "Female and Male Left Handers",ylab = "Count" ,col = c("red","blue"))
```
## 4.Draw the histogram of age distribution with the title as „Age distribution‟ and xlabel
as „Age range‟ and ylabel as „frequency‟.
```{r}
freq = table(newsurvey$Age)
hist(freq, main = "Age Distribution", xlab = "Age Range", ylab = "Frequency", col = c("blue", "green"))
```
## 5.Reveal the relationship between the age and writing hand span using scatter plot.
```{r}
plot(newsurvey$Age, newsurvey$Wr.Hnd)
```

## 6.Draw the boxplot for pulse rate to analyse the five summary statistics. Provide
appropriate title and label. 

```{r}

boxplot(newsurvey$Pulse, main = "Pulse Rate Statistics",ylab = "Pulse Rate",col = "red")
summary(newsurvey$Pulse)
```
## 7.Draw the distribution of smoking habits of male left handers using pie chart.
```{r}
M_L = d1 %>% filter(Sex == "Male")
count = table(M_L$Smoke)
pie(count, main = "Male Left Hand Smokers")
```
```{r}
file1 <- read.csv("/home/ex5/Desktop/22mia1049/Sample Datasets-20230926/iris.csv")
data1 = na.omit(file1)
data1
```
## Correalation Analysis
```{r}
plot(file1,main = "Iris Dataset")
```
## Outliers
```{r}
boxplot(data1[,2:6], "Outliers")
```
## Plot the frequency table
```{r}
freq = table(data1$species)
plot(freq,main = "Frequency")
```

